---
title: "Ontario Senior Income & GAINS Benefits"
subtitle: "Statistical Analysis in R"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
source("R/00_setup.R")
```

# Project Objective

This project evaluates how minimum annual private income relates to Ontario GAINS support and minimum total monthly income across the published GAINS benefit-rate schedule for seniors aged 75+.

> **Data limitation:** the source is a benefit-rate table, not a random sample of individual recipients. Inferential procedures are therefore used primarily to demonstrate statistical methods and compare segments of the published schedule.

# Data Preparation

```{r cleaning}
source("R/01_data_cleaning.R")
```

# Exploratory Analysis

```{r eda}
source("R/02_exploratory_analysis.R")
```

# Hypothesis Testing

The revised test consistently compares **minimum total monthly income** across groups defined by **minimum annual private income** using a $7,500 threshold.

```{r hypothesis}
source("R/03_hypothesis_testing.R")
```

# Bootstrap Resampling

The bootstrap evaluates the stability of the mean across schedule rows. It should not be interpreted as a conventional population confidence interval because the rows are not sampled individuals.

```{r bootstrap}
source("R/04_bootstrap_analysis.R")
```

# Regression Analysis

```{r regression}
source("R/05_regression_analysis.R")
```

# Model Validation and Leakage Review

The original assignment predicted total monthly income using all remaining columns. Because minimum total monthly income is exactly reconstructed by combined OAS/GIS + GAINS + minimum monthly private income, that design leaks the target into the predictors. The revised validation cross-validates the simpler `GAINS ~ annual_private_min` model instead.

```{r validation}
source("R/06_model_validation.R")
```

# Conclusion

The project demonstrates a complete statistical workflow while highlighting two professional lessons: statistical significance is not the same as predictive strength, and implausibly perfect validation performance can indicate target leakage rather than a superior model.
